Machine Learning Methods for Discourse Segmentation of Communications in E-Mail Based Behavioral Interventions

### 2018-07-25 paper-amia-summit-2018/manuscript.tex
update results

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM and KNN methods for identification of ``new segment'' and ``same segment'' classes as well as their weighted average. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_base}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{new segment}} & \multicolumn{3}{|c|}{\textbf{same segment}}  & \multicolumn{3}{|c|}{\textbf{overall}} \\\cline{2-10}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline    
 \multicolumn{10}{|c|}{lexical features only} \\ \hline   
 NB & 0.594 & 0.662 & 0.626 & 0.988 & 0.985 & 0.987 & 0.975 & 0.974 & 0.975  \\ \hline
 SVM & 0.721 & \textbf{0.705} & 0.713 & \textbf{0.990} & 0.991 & 0.990  & 0.981 & 0.981 & 0.981 \\ \hline
 KNN & \textbf{0.808} & 0.663 & \textbf{0.728} & 0.989 & \textbf{0.995} & \textbf{0.992} & \textbf{0.983} & \textbf{0.984} & \textbf{0.983} \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM and KNN methods with different topic model-based features for segmentation of e-Coaching emails as a weighted average over ``same segment'' and ``new segment'' classification results, when all features are used together. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
  \begin{tabular}{|l|l|l|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{L-LDA-based topic features}} & \multicolumn{3}{|c|}{\textbf{DL-LDA-based topic features}}  & \multicolumn{3}{|c|}{\textbf{LCA-based topic features}} \\\cline{2-10} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1}\\ \hline

 NB & 0.975 & 0.973 & 0.974 & 0.975 & 0.973 & 0.974 & 0.975 & 0.974 & 0.975 \\ \hline
 SVM & 0.987 & 0.988 & 0.987 & \textbf{0.990} & \textbf{0.990} & \textbf{0.990} & 0.989 & 0.989 & 0.989 \\ \hline
 KNN & 0.985 & 0.986 & 0.985 & 0.985 & 0.986 & 0.985 & 0.985 & 0.986 & 0.986 \\ \hline
  \end{tabular}
\end{table}

@@

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics[width=1.0\textwidth]{figures/CRNN.eps}
    \caption{\textbf{Receiver operating characteristic curves showing the performance of binary classifiers for the segmentation of e-Coaching text when lexical features (left) and combination of lexical, DL-LDA-based topic (except LSTM and GRU) and punctuation features (right) are used}.}
    \label{fig:crnn}
\end{figure}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM and KNN methods for identification of ``new segment'' and ``same segment'' classes as well as their weighted average. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_base}
  \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{new segment}} & \multicolumn{3}{|c|}{\textbf{weighted macro average}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Measure} \\ \hline    
 CRF & 0.782 & 0.691 & 0.733 & 0.983 & 0.984 & 0.984 \\ \hline
 MLP & \textbf{0.836} & 0.593 & 0.694 & 0.982 & 0.983 & 0.982 \\ \hline
 BRNN & 0.606 & 0.680 & 0.641 & 0.977 & 0.976 & 0.976 \\ \hline
 CRNN & 0.775 & \textbf{0.797} & \textbf{0.785} & \textbf{0.986} & \textbf{0.986} & \textbf{0.986} \\ \hline
  \end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Performance of NB, SVM and KNN methods with different topic model-based features for segmentation of e-Coaching emails as a weighted average over ``same segment'' and ``new segment'' classification results, when all features are used together. The highest value for each performance metric is highlighted in bold.}
\label{tab:result_weighted_avg}
 \begin{tabular}{|l|l|l|l|l|l|l|}
  \hline
   \multirow{2}{*}{\textbf{Method}} & \multicolumn{3}{|c|}{\textbf{new segment}} & \multicolumn{3}{|c|}{\textbf{weighted macro average}} \\\cline{2-7}
   & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Measure} & \textbf{Precision}  & \textbf{Recall} & \textbf{F1-Measure} \\ \hline    
 CRF & 0.813 & 0.772 & 0.792 & 0.988 & 0.988 & 0.988 \\ \hline
 MLP & \textbf{0.814} & 0.732 & 0.771 & 0.987 & 0.987 & 0.987 \\ \hline
 BRNN & 0.683 & 0.820 & 0.745 & 0.985 & 0.983 & 0.984 \\ \hline
 CRNN & 0.789 & \textbf{0.864} & \textbf{0.825} & \textbf{0.990} & \textbf{0.989} & \textbf{0.989} \\ \hline
  \end{tabular}
\end{table}

@@

% Baseline ROC results: BRNN: 0.9198, MLP: 0.9507, CRF: 0.9662, CRNN: 0.9648
% Proposed ROC Results: BRNN: 0.9807, MLP: 0.992, CRF: 0.9937, CRNN: 0.9859
